A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-16 draft.tex
Eliminates repetitive sentence

We preferred the use of a container-based implementation for this prototype because
it is more suitable for development and replication without needing
additional components. Nevertheless, the application is compatible with other
orchestration and deployment technologies if more scalability is needed. 
With additional configuration settings, applications can be deployed 
to a Docker Swarm or a Kubernetes system.
%% Here we could talk about Cloud-based platform for executing the application
%% and the cloud-lock risk - Mario

>>>>

% ------------------------ Commented this out since this is said
% elsewhere ----------------------------------------------------
% We preferred the use of a container-based implementation for this prototype because
% it is more suitable for development and replication without needing
% additional components. Nevertheless, the application is compatible with other
% orchestration and deployment technologies if more scalability is needed. 
% With additional configuration settings, applications can be deployed 
% to a Docker Swarm or a Kubernetes system.
%% Here we could talk about Cloud-based platform for executing the application
%% and the cloud-lock risk - Mario
